---
title: "regression"
author: Lei Huang
format: html
editor: visual
---

## 1. Aim

This workflow generates simulated data and explores the relationship between two variables. It demonstrates how text, R code, and results can be combined in a reproducible report.

## 2. Data generation

The data are simulated and do not represent real observations. Both variables are dimensionless.

We generate 100 observations using the following model:

$$
y_i = 2 + 3x_i + \varepsilon_i
$$

where:

$$
x_i \sim \mathrm{Uniform}(0, 10),
\qquad
\varepsilon_i \sim N(0, 2^2).
$$

The random errors are generated independently of x. A fixed random seed is used to make the simulation reproducible under the same random-number settings.

```{r}
# Set the random seed
set.seed(123)

# Generate the simulated data
n <- 100
x <- runif(n, min = 0, max = 10)
error <- rnorm(n, mean = 0, sd = 2)
y <- 2 + 3 * x + error

# Store the data
sim_data <- data.frame(x = x, y = y)

# Export the simulated data in a common format
write.csv(sim_data, "simulated_data.csv", row.names = FALSE)

# Display the first six observations
head(sim_data)
```

## 3. Summary statistics

The following output summarises the two simulated variables.

```{r}
summary(sim_data)
```

## 4. Visualisation

The scatter plot shows the relationship between x and y. The red line represents the mean relationship used to generate the data. It is not fitted to the observations.

```{r}
# Plot the simulated observations
plot(
  sim_data$x, sim_data$y,
  main = "Simulated linear relationship",
  xlab = "x",
  ylab = "y",
  pch = 19,
  col = "steelblue"
)

# Add the true mean relationship
abline(a = 2, b = 3, col = "red", lwd = 2)
```

The observations show a positive relationship between x and y. They vary around the red line because the model includes random error.

## 5. Software requirements and version pinning

This workflow was tested on Windows using R 4.3.3 and Quarto 1.5.57.
The simulation, summary statistics, and plot use functions included
with R. Report rendering requires knitr and rmarkdown, together
with their dependencies.

The R package versions are recorded in renv.lock.
Exact package versions are used to reduce differences caused by
package updates and to help other users recreate the tested environment.

To reproduce this workflow:

1. Install R 4.3.3 and Quarto 1.5.57.
2. Download the complete project and open its RStudio project file.
3. Run the following command in the R Console to restore the
   recorded R package versions:

```r
renv::restore()
```

4. Render analysis.qmd using the Render button in RStudio,
   or run the following command in a terminal from the project folder:

```bash
quarto render analysis.qmd
```

The renv lockfile records the R version, but renv does not install R
or Quarto. These tools must be installed separately.
An internet connection is normally needed to download the required
packages during setup.

The following output records the R session used to render this report.

```{r}
sessionInfo()
```

## 6. Risk assessment

The analysis uses functions included with R and has few external
dependencies. This reduces the number of packages that could affect
the numerical results. However, changes to R or its random-number
settings could affect the simulated data.

Report generation also depends on Quarto, knitr, rmarkdown, and
their dependencies. Future updates could change the report appearance
or cause rendering errors. Using the tested software versions and
restoring the recorded package versions reduces these risks.

Version pinning does not guarantee that the workflow will always run.
Older package versions may become harder to obtain or install.
Installation on another operating system may require additional
system tools. This workflow has only been tested on Windows.

Before updating the recorded environment, the complete report should
be rendered again. The generated data, summary statistics, and plot
should be compared with the previous output. The lockfile should only
be updated after checking that the revised environment works.

## 7. Discussion of FAIR principles

FAIR stands for Findable, Accessible, Interoperable, and Reusable.
This section discusses how the workflow supports these principles
and what still needs to be completed.

### Findable

The report has a descriptive title and identifies its author.
The project will be shared on GitHub with a README, a short
description, and relevant keywords, such as R, simulation,
reproducibility, and FAIR.

These details will help users find and understand the project.
However, the project does not currently have a persistent identifier,
such as a DOI.

### Accessible

The planned public GitHub repository will allow users to download
the source document, simulated data, and environment files.
The HTML report will allow users to read the results without
running R.

The workflow generates its own data and does not require access
to an external dataset. However, long-term access will depend on
the repository remaining available.

### Interoperable

The simulated data are exported as a CSV file, which can be read
by different software tools. Each row represents one simulated
observation. The columns x and y are numeric and have no physical
units. Their definitions and the data-generation model are
provided in this report.

The source document uses plain text, and the report is available
in HTML. These formats support exchange between tools.
However, the project does not use a formal metadata vocabulary,
so its support for automated interpretation is limited.

### Reusable

The report explains the simulation model, sample size, random seed,
and analysis steps. The data are clearly identified as simulated.
The software requirements and renv.lock help users recreate
the tested environment.

A license and README still need to be added before sharing.
These will clarify the permitted uses and explain how to run
the project. The simulated data are suitable for demonstrating
a workflow, but they do not provide evidence about a real-world
relationship.
